Descriptive, not injunctive, social norms caused increases in mask wearing during the COVID-19 pandemic

### 2023-03-27 manuscript.Rmd
update ethics statement and README

This project was granted exemption from the Institutional Review Board of Arizona State University (STUDY00011678). All participants in this study provided informed consent.

>>>>

All experimental protocols were approved by the Institutional Review Board of Arizona State University (STUDY00011678). All methods were carried out in accordance with relevant guidelines and regulations. All participants in this study provided informed consent.
